%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ATS-Friendly One-Page Resume (Final Compact Version)
%
% This template has been updated to prevent single-word line wraps
% by widening the text area and carefully trimming content for conciseness.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, a4paper]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[left=0.45in, right=0.45in, top=0.4in, bottom=0.4in]{geometry} % Wider text area
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% --- FORMATTING ---
\pagestyle{empty} % No page numbers
\setlength{\parindent}{0pt} % No paragraph indentation

% Define colors and links
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

% Format section titles with less space
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

% Make all lists tight
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=0pt, parsep=2pt}


% --- DOCUMENT START ---
\begin{document}

% --- HEADER ---
\begin{center}
    \textbf{\huge TANMAY KAPURE}
    \vspace{3pt}
    
    tk427@njit.edu $\cdot$ +1 (862) 405-2014 $\cdot$ \href{https://www.linkedin.com/in/tanmay-kapure/}{linkedin/tanmay-kapure} $\cdot$ \href{https://tanmaysk001.github.io/tanmaykapure.github.io/}{Personal Website} $\cdot$ New York, NY, USA
\end{center}


% --- SUMMARY ---
\section*{Summary}
AI Engineer with hands-on expertise in building end-to-end production grade ML pipelines, fine-tuning and optimizing LLMs, and developing AI agents with cutting-edge frameworks, backed by strong collaboration and team leadership skills.

\vspace{2pt}
% --- TECHNICAL SKILLS ---
\section*{Technical Skills}
\noindent\textbf{Programming Languages:} Python, SQL, JavaScript, R, Go  \\
\textbf{Frameworks \& Packages:} PySpark, TensorFlow, Keras, Pytorch, Hugging Face, Django, FastAPI, LangChain, LangFlow, Langgraph, NextJS  \\
\textbf{Tools \& Platforms:} Kafka, Airflow, Azure, AWS, Docker, Tableau, PowerBI, Git, Excel, MySQL, PineCone DB, Firebase, Supabase

\vspace{2pt}
% --- WORK EXPERIENCE ---
\section*{Work Experience}
\vspace{2pt}

\textbf{Machine Learning Engineer} \hfill Oct 2024 – Present \\
\textit{New Jersey Institute of Technology (NJIT) - U.S. Army-Funded Research} \hfill Newark, USA
\begin{itemize}
    \item Developed deep learning models to predict metal fatigue strength, incorporating advanced architectures like Transformers.
    \item Improved prediction accuracy, reducing Mean Relative Error (MRE) from 140 \% to 60 \%. 
    \item Implemented state-of-the-art deep learning research for fatigue strength prediction. 
\end{itemize}
\vspace{2pt} % Reduce space between entries

\textbf{Research Assistant} \hfill Mar 2024 – Oct 2024 \\
\textit{Center of Solar and Terrestrial Research, NJIT - NASA \& NSF Funded Projects} \hfill Newark, USA
\begin{itemize}
    \item Transformed 500,000+ raw solar surface images using advanced image processing into 500+ high quality videos.
    \item Collaborated with a multidisciplinary team of 15+ researchers to facilitate extraction of solar imagery information. 
    \item Conducted testing, debugging, and code integration for parallel ray tracing simulations on an HPC cluster. 
\end{itemize}
\vspace{2pt} % Reduce space between entries

\textbf{Machine Learning Intern} \hfill March 2023 - August 2023 \\
\textit{Everlytics Data Science Pvt Ltd.} \hfill Bengaluru, India
\begin{itemize}
    \item Implemented an AWS Glue job scheduling pipeline, increasing the efficiency of data extraction by 30\%.
    \item Deployed a robust Isolation Forest anomaly detection model, mitigating 95\% of anomalies and 25 \% of false positives. 
    \item Optimized Apache Airflow data pipelines, processing ~1M rows/week and improving reliability 20\% with MLOps. 
\end{itemize}
\vspace{2pt} % Reduce space between entries

\textbf{Data Science Intern} \hfill Nov 2022 – Mar 2023 \\
\textit{Jubilant Biosys Ltd.} \hfill Bengaluru, India
\begin{itemize}
    \item Optimized forecasting models (Random Forest, ARIMA) to 91\% accuracy, cutting overstocking by 20 \% and understocking by 15\%.
    \item Designed 5 interactive Tableau dashboards, increasing data visibility by 40 \% and enabling real-time KPI tracking. 
    \item Executed A/B testing to optimize inventory strategies, reducing stockouts by 10\% and improving order fulfillment 5\%. . 
\end{itemize}

\vspace{4pt}

% --- RELEVANT PROJECTS ---
\section*{Relevant Projects}
\vspace{2pt}
\textbf{RAG based AI Chatbot for Intelligent Document Retrieval} \hfill \href{https://huggingface.co/spaces/Tsk001/RAG_Gradio_App}{Live Project Link}
\begin{itemize}
    \item Built an end-to-end RAG system with LangChain, FastAPI, and Pinecone to enable context-aware LLM responses.
    \item Enhanced document processing and chunking using sentence transformers and created a Gradio webapp for interaction. 
    \item Orchestrated the webapp on Hugging Face Spaces with Docker \& CI/CD for scalability and real-time query handling. 
\end{itemize}
\vspace{2pt}

\textbf{Browser AI Agent} \hfill \href{https://github.com/tanmaysk001/Browser-Agent}{Live Project Link}
\begin{itemize}
    \item Created a browser agent using Langgraph, Gemini, and Playwright to navigate and extract info from web pages. 
    \item Features captcha bypass, website scraping, and a Human in the Loop capability to fulfill browser tasks. 
    \item Smart LLM assisted navigation to successfully handle dynamically changing web layouts
\end{itemize}
\vspace{2pt}

\textbf{Voice AI Interview Assistant} \hfill \href{https://github.com/tanmaysk001/Interview-AI}{Live Project Link}
\begin{itemize}
    \item Developed a full-stack Voice AI agent to simulate mock interviews using VAPI AI and Gemini APIs.
    \item Intelligent chatbot that provides performance-based feedback to aid interview preparation. 
    \item Responsive frontend based on Next.js and Tailwind CSS, while PostgreSQL for database and Firebase for authentication, hosted on Vercel. 
\end{itemize}

\vspace{4pt}
% --- EDUCATION ---
\section*{Education}

\textbf{MS in Data Science (GPA: 3.91)} \hfill Sep 2023 – May 2025 \\
\textit{New Jersey Institute of Technology} \hfill Newark, USA \\
\textsc{}{ Statistical modeling, Supply Chain Management (SCM), Data mining, Deep Learning in Finance, Big Data analytics}

\vspace{2pt}

\textbf{B.Tech in Artificial Intelligence (GPA: 3.76)} \hfill Aug 2019 – June 2023 \\
\textit{Nagpur University} \hfill Nagpur, India \\
\textsc{}{ DSA, DBMS, Software Engineering, Machine Learning, Computer Vision, Natural Language Processing, AI Analytics}

\end{document}